Multiset-Trie Data Structure

### 2023-03-20 tex/algorithms-2122309-proof.tex
changes in mathematical section

Our model assumes that all the inserted multisets are chosen with the same probability,
meaning that for some $p\in (0,1)$, the following holds:
\[
P(m\in M) = p, \quad \forall~m\in N.
\]
%
\hl{Let} %MDPI: Whether the indentation of the paragraph after the formula is necessary, please confirm. Please check all.
 $\xi_1, \xi_2, \ldots, \xi_{\sigma+1}$ be random variables such that $\xi_i$
represents the number of nodes in a multiset-trie on the $i$-th level. For every node $j$ 
on $i$-th level, we assign a random variable $\xi_{ij}$ to be the number of its children, 
such that $j\in[1,\xi_i].$ Then, for every $i\in[1,\sigma]$, the following~holds:%
\begin{equation}\label{eq:sum_recursive}
\xi_{i+1} = \sum_{j=1}^{\xi_i} \xi_{ij},
\end{equation}
%
where $\xi_1 = 1.$
%
It is easy to see that the variable $\xi_{i+1}$ can have values in the interval
$[\xi_i,n^{i}]$ and the value of the variable $\xi_{ij}$ is within the interval $[1,n].$
Without conditioning on the existence of any node in multiset-trie, 
it is easy to describe the probability of the existence of any individual node.

@@

\includegraphics[width=.64\textwidth, keepaspectratio]{exp-nodes-on-probab.pdf}
\caption{\hl{Size} %MDPI: Please change the terms into scientific notations in the figure,  e.g., "$8 \times 10^{3}$", not "8E3".
 of a tree ($\mathbb{E}(|\mathcal{M}|)$) compared to the number of stored sets ($\mathbb{E}(|M|)$), as the probability parameter $p$ increases.
Parameters 
$\sigma$ and $n$ are $26$ and $10,$ respectively.
The additional overhead space that our data structure uses does not increase as the tree is becoming more and more dense.
}
\label{f:exp-nodes}
\end{figure}

@@

\includegraphics[width=.64\textwidth, keepaspectratio]{ratio-exp-nodes-and-msets-on-prob.pdf}
\caption{The ratio of ``data overhead'' derived from Figure \ref{f:exp-nodes}, as the density $p$ of our data structure increases.
Unless we are in a very sparse setting, the trade-off in terms of space is small.}
\label{f:ratio-exp-msets}
\end{figure}

@@

\subsection{Data%MDPI: Section headings should be numbered sequentially, e.g., Section 2.1, Section 2.2.1. Please confirm this revision. %RES It is Ok as it is.
 Generation}
We denote by \emph{input data} the data that are used to fill the structure prior 
to testing and by \emph{test data} the set of queries that are used to test the 
performance of the functions.

>>>>

Our model assumes that all the inserted multisets are chosen with the same probability,
meaning that for some $p\in (0,1)$, the following holds:
\[
P(m\in M) = p, \quad \forall~m\in N.
\]
%
Let % MDPI: Whether the indentation of the paragraph after the formula is necessary, please confirm. Please check all.
%RES: We do not want to start new paragraph here, hence no indentation!
 $\xi_1, \xi_2, \ldots, \xi_{\sigma+1}$ be random variables such that $\xi_i$
represents the number of nodes in a multiset-trie on the $i$-th level. For every node $j$ 
on $i$-th level, we assign a random variable $\xi_{ij}$ to be the number of its children, 
such that $j\in[1,\xi_i].$ Then, for every $i\in[1,\sigma]$, the following~holds:%
\begin{equation}\label{eq:sum_recursive}
\xi_{i+1} = \sum_{j=1}^{\xi_i} \xi_{ij},
\end{equation}
%
where $\xi_1 = 1.$
%
It is easy to see that the variable $\xi_{i+1}$ can have values in the interval
$[\xi_i,n^{i}]$ and the value of the variable $\xi_{ij}$ is within the interval $[1,n].$
Without conditioning on the existence of any node in multiset-trie, 
it is easy to describe the probability of the existence of any individual node.

@@

\begin{figure}[H]
\centering
\includegraphics[width=.64\textwidth, keepaspectratio]{exp-nodes-on-probab-1.pdf}
\caption{Size % MDPI: Please change the terms into scientific notations in the figure,  e.g., "$8 \times 10^{3}$", not "8E3". %RES: done.
 of a tree ($\mathbb{E}(|\mathcal{M}|)$) compared to the number of stored sets ($\mathbb{E}(|M|)$), as the probability parameter $p$ increases.
Parameters 
$\sigma$ and $n$ are $26$ and $10,$ respectively.
The additional overhead space that our data structure uses does not increase as the tree is becoming more and more dense.
}
\label{f:exp-nodes}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.64\textwidth, keepaspectratio]{ratio-exp-nodes-and-msets-on-prob.pdf}
\caption{The ratio of ``data overhead'' derived from Figure \ref{f:exp-nodes}, as the density $p$ of our data structure increases.
Unless we are in a very sparse setting, the trade-off in terms of space is small.}
\label{f:ratio-exp-msets}
\end{figure}

@@

\subsection{Data %MDPI: Section headings should be numbered sequentially, e.g., Section 2.1, Section 2.2.1. Please confirm this revision. %RES It is Ok as it is.
 Generation}
We denote by \emph{input data} the data that are used to fill the structure prior 
to testing and by \emph{test data} the set of queries that are used to test the 
performance of the functions.
